### 2015-06-05 Manuscript/Missing_mammals-draft.tex
Edits to figure legend

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{example_coverage.pdf}
\caption{Phylogenetic distribution of available cladistic data across two mammalian orders (A: Cetartiodactyla; B: Carnivora).
Edges are colored in grey when no cladistic data is available or in red when data is available.}
\label{Figure_example_coverage}
\end{figure}
% NC: Can we change the colours, red sucks. Otherwise I like the figure a lot.
% TG: Again, will fix in the final version.

>>>>

\begin{figure}[!htbp]
\centering
    \includegraphics[width=1\textwidth]{example_coverage.pdf}
\caption{Phylogenetic distribution of species with available cladistic data across two mammalian orders (A: Cetartiodactyla; B: Carnivora).
Edges are colored in grey when no cladistic data is available for a species or in blue when data is available.}
\label{Figure_example_coverage}
\end{figure}
